A novel route to the spontaneous formation of porous crystals via viscoelastic phase separation

### 2016-06-14 crystal-gel/talk_Roscoff.tex
Change tree structure

\institute[iLM]{iLM, Univ. Claude Bernard Lyon 1 and CNRS, France}
\title[crystal gel]{A novel route to the spontaneous formation of porous crystals via viscoelastic phase separation}
\author[M. Leocmach]{Mathieu Leocmach}
\date{30 June 2016}
\titlegraphic{
	\begin{tabu}{X[c]X[c]X[c]}
		\includegraphics[height=3\baselineskip]{Tsurusawa}&
		\includegraphics[height=3\baselineskip]{John}&
		\includegraphics[height=3\baselineskip]{Tanaka}\\
		Hideyo Tsurusawa & John Russo & Hajime Tanaka\\
		U. Tokyo & U. Bristol & U. Tokyo\\
	\end{tabu}

@@

\begin{frame}{Crystallisation}
	\tikzsetnextfilename{whyx}%
	\input{fig_presentation/whyx.pgf}

@@

\begin{frame}{Let it snow!}
	\hfill Wegener-\alert{Bergeron}-Findeisen \alert{process}
	\begin{columns}[b]
	\column{0.4\textwidth}
	\includegraphics[width=\textwidth,clip=true,trim=0 0 0 1cm]{Pitter1.jpg}

	\vspace{1em}\includegraphics[width=\textwidth]{bergeron.jpg}
	\column{0.40\textwidth}
	\includegraphics[width=\textwidth,clip=true,trim=0 0 0.8mm 0]{queries-figure-1.jpg}

	\vspace{1em}\includegraphics[width=\textwidth]{OKC-Fallstreak.jpg}
	\end{columns}
\end{frame}

@@

	\bigskip
	\includegraphics[width=\textwidth]{../../CNRS-2015/Renth_sedim.jpg}\\
	\textit{\footnotesize Poon PRL 1999, Renth PRE 2001}
	\begin{itemize}
	\item triple coexistence
	\item various kinetic paths
	\end{itemize}

	\column{0.45\textwidth}
	\includegraphics[width=\textwidth,clip=true,trim=0 0 0 4.5cm]{Renth_diag.pdf}
	\end{columns}
\end{frame}

\begin{frame}{Another class of gel? Crystal-gel?}
	\begin{itemize}
	\item Phase separation arrested by crystallisation
	\begin{description}
		\item[polymer blend] Tanaka \& Nishi \textit{PRL} 1985
		\item[simulations] Soga \textit{J.Chem. Phys.} 1999; Fortini \textit{PRE} 2008 
	\end{description}
	\item Spinodal then crystallisation
	\begin{description}
		\item[simulations] Pérez \textit{Langmuir} 2011
		\item[microgravity] (triple coexistence) Sabin \textit{PRL} 2012
	\end{description}
	\end{itemize}
	\includegraphics[width=\textwidth]{micrograv_Sabin2012}
\end{frame}

\begin{frame}{Experimental}
How to do that in 3D at particle level \alert{without a space station}?
\begin{itemize}
\item index matched + \alert{\SI{2.3}{\micro\metre} colloids} + confocal
\item density match + $T$-control
\item preparation protocol without flow
\end{itemize}
\bigskip
\begin{columns}
	\column{0.265\textwidth}
		Colloids+polymers\\
		{\footnotesize no screening
		\begin{itemize}
			\item Dispersed
			\item Homogeneous
		\end{itemize}
		\bigskip
		\begin{beamercolorbox}[rounded=true]{block body}PMMA + PS\\
		in decalin + CHB $\epsilon_r\approx5$\\
		$\kappa^{-1}>\SI{10}{\micro\metre}$
		\end{beamercolorbox}}
	\column{0.4\textwidth}
		\tikzsetnextfilename{chemin_gelification}%
		\input{chemin_gelification.pgf}
	\column{0.335\textwidth}
		\tikzsetnextfilename{cell}%
		\input{cell.pgf}
\end{columns}
\end{frame}

\begin{frame}{Exploring phase diagram}
	\vspace{\baselineskip}
	\tikzsetnextfilename{phdiag_cluster}%
	\begin{tikzpicture}[
		every axis/.style={
		xlabel absolute, every axis x label/.append style={anchor=base, yshift=-1em},
		%ylabel absolute, every axis y label/.append style={anchor=base, yshift=-0.5em}
		}]
	\pgfplotscreateplotcyclelist{samples}{%
	blue,mark=square*,\\%
	cyan,mark=square\\%
	red, thick, mark=*\\%
	red!65!yellow, mark=otimes\\%
	red!30!yellow, mark=oplus\\%
	red!65!black, mark=o\\%
	}%
	\begin{groupplot}[
		group style={
				group name=g, group size=2 by 2,
				horizontal sep=4em,
				vertical sep=3em,
				%x descriptions at=edge bottom,
			},
		cycle list name=samples,
		width=0.51\textwidth,
		height=0.5\linewidth,
		axis on top,
	]
	\nextgroupplot[
		title={phase diagram},
		xlabel={$\phi$}, ylabel={$c_p$ (\si{\milli\gram/\gram})},
		xmin=0,xmax=0.74,
		ymin=0, ymax=1.9, ytick={0,0.5,...,2},
		mark options={solid}
		]
		\begin{scope}[dotted, mark repeat=2,mark phase=2,<->]
		\addplot file {/data/Documents/tex/svn/crystal-gel/sample0.phd};
		\addplot file {/data/Documents/tex/svn/crystal-gel/sample1.phd};
		\addplot file {/data/Documents/tex/svn/crystal-gel/sample2.phd};
		\addplot file {/data/Documents/tex/svn/crystal-gel/sample3.phd};
		\addplot file {/data/Documents/tex/svn/crystal-gel/sample4.phd};
		\addplot file {/data/Documents/tex/svn/crystal-gel/sample5.phd};
		\end{scope}
		\addplot[black, dashed,no marks] file {/data/Documents/tex/svn/crystal-gel/gasliquid_sg.phd};% node[diamond, fill, inner sep=2pt] at (current plot begin){};
		\addplot[black, dashed,no marks] file {/data/Documents/tex/svn/crystal-gel/gasliquid_sl.phd};
		\addplot[black, no marks] file {/data/Documents/tex/svn/crystal-gel/gasliquid_bl.phd};
		\addplot[black, no marks] file {/data/Documents/tex/svn/crystal-gel/gasliquid_bg.phd};
		\addplot[fill=lightgray!50, no marks, draw=none] file {/data/Documents/tex/svn/crystal-gel/fluidcrystal_f.phd} node[above right] at (rel axis cs:0,0) {Fluid} -- (rel axis cs:0,0) \closedcycle;
		\addplot[fill=lightgray!50, no marks, draw=none] file {/data/Documents/tex/svn/crystal-gel/fluidcrystal_x.phd} node[above left] (x) at (rel axis cs:1,0.5) {Crystal}  -| (rel axis cs:1,0) \closedcycle;
		%\draw[gray] (axis cs:0.371290311343, 0.12299370925) -- (axis cs:0.680497991395,0.0372636873433);
		%\draw[gray, dotted] (axis cs:3.40152108798e-05,0.624739653238) -- (axis cs:0.722831684246, 0.0726528862772);
		\draw[->] (x.base) --(rel axis cs:0.98,0.01);
		\addplot[only marks, mark=triangle] file{/data/Documents/tex/svn/crystal-gel/fluid_samples.phd};

	\nextgroupplot[
		title={cluster size distribution},
		xlabel={$s$}, ylabel={$R_g/\sigma$},
		xmin=1, xmax=4e3,
		ymin=0.5, ymax=30,
		xmode=log, ymode=log, 
		clip mode=individual,
		]
		\addplot file{/data/Documents/tex/svn/crystal-gel/data/fig1b_sqrt_1.dat};
		\addplot file{/data/Documents/tex/svn/crystal-gel/data/fig1b_sqrt_2.dat};
		\addplot file{/data/Documents/tex/svn/crystal-gel/data/fig1b_sqrt_3.dat};
		\addplot file{/data/Documents/tex/svn/crystal-gel/data/fig1b_sqrt_4.dat};
		\addplot file{/data/Documents/tex/svn/crystal-gel/data/fig1b_sqrt_5.dat};
		\addplot[gray, ultra thick, domain=1:4e3] {0.629*x^(1/2.53)} node [left] at (rel axis cs:1,0.9){$D=2.53$};

@@

\begin{frame}{Outlier at later times}
	\vspace{\baselineskip}
	\tikzsetnextfilename{Sq_localphi}%
	\begin{tikzpicture}[
		every axis/.style={
		xlabel absolute, every axis x label/.append style={anchor=base, yshift=-1em},
		%ylabel absolute, every axis y label/.append style={anchor=base, yshift=-0.5em}
		}]
	\pgfplotscreateplotcyclelist{samples}{%
	blue,mark=square*,\\%
	cyan,mark=square\\%
	red, thick, mark=*\\%
	red!65!yellow, mark=otimes\\%
	red!30!yellow, mark=oplus\\%
	red!65!black, mark=o\\%
	}%
	\begin{groupplot}[
		group style={
				group name=g, group size=2 by 2,
				horizontal sep=4em,
				vertical sep=3em,
				%x descriptions at=edge bottom,
			},
		cycle list name=samples,
		width=0.51\textwidth,
		height=0.5\linewidth,
		axis on top,
	]
	\nextgroupplot[
		title={structure factor},
		xlabel={$q\sigma$}, ylabel={$S(q)$},
		xmode=log, ymode=log, xmin=0.2, xmax=20, ymin=0.1,
		restrict x to domain=-1.8:3, unbounded coords=discard, 
		%clip mode=individual
		]
		\addplot+[clip mode=individual] file{/data/Documents/tex/svn/crystal-gel/data/fig3c_1.dat};
		\addplot+[clip mode=individual] file{/data/Documents/tex/svn/crystal-gel/data/fig3c_2.dat};
		\addplot file{/data/Documents/tex/svn/crystal-gel/data/fig3c_3.dat};
		\addplot+[clip mode=individual] file{/data/Documents/tex/svn/crystal-gel/data/fig3c_4.dat};
		\addplot+[clip mode=individual] file{/data/Documents/tex/svn/crystal-gel/data/fig3c_5.dat};
		\addplot[black, ultra thick, domain=0.1:3] {2.14605*x^(-3)} node[pos=0.92,left=0.5em] {$D=3$};
		\addplot[gray, ultra thick, domain=0.1:3] {3.98797*x^(-2.53)} node [pos=0.65, above right] {$D=2.53$};

	\nextgroupplot[
		title={local volume fraction},
		xlabel={\# neighbours}, ylabel={$\phi$ [\%]},
		xmin=0, ymin=0, ytick={0,10,30,50},
		extra y ticks={64, 72}, extra y tick style={grid=major}, extra y tick label={},
		legend pos=north west, legend style={font=\footnotesize},
		no markers,
		/pgfplots/error bars/y dir=both, /pgfplots/error bars/y explicit,
		]
		\addplot table[y error=err]{/data/Documents/tex/svn/crystal-gel/data/vol_err_phi_0.10_cp_0.82.scaled};
		\addplot table[y error=err]{/data/Documents/tex/svn/crystal-gel/data/vol_err_phi_0.10_cp_1.36.scaled};
		\addplot table[y error=err]{/data/Documents/tex/svn/crystal-gel/data/vol_err_phi_0.25_cp_0.38.scaled};
		\addplot table[y error=err]{/data/Documents/tex/svn/crystal-gel/data/vol_err_phi_0.25_cp_0.48.scaled};
		\addplot table[y error=err]{/data/Documents/tex/svn/crystal-gel/data/vol_err_phi_0.25_cp_0.57.scaled};

@@

\begin{frame}{Real space: crystal gel!}
	\tikzsetnextfilename{phdiag_arrows}%
	\begin{tikzpicture}[
			every axis/.style={
			xlabel absolute, every axis x label/.append style={anchor=base, yshift=-1em},
			%ylabel absolute, every axis y label/.append style={anchor=base, yshift=-0.5em}
			}]
		\pgfplotscreateplotcyclelist{samples}{%
		blue,mark=square*,\\%
		cyan,mark=square\\%
		red, thick, mark=*\\%
		red!65!yellow, mark=otimes\\%
		red!30!yellow, mark=oplus\\%
		red!65!black, mark=o\\%
		}%
		\begin{axis}[
			cycle list name=samples,
			width=0.51\textwidth,
			height=0.5\linewidth,
			axis on top,
			xlabel={$\phi$}, ylabel={$c_p$ (\si{\milli\gram/\gram})},
			xmin=0,xmax=0.74,
			ymin=0, ymax=1.9, ytick={0,0.5,...,2},
			mark options={solid}
			]
			\begin{scope}[/pgfplots/skip coords between index={0}{1}, /pgfplots/skip coords between index={2}{3}]%[draw=none,mark repeat=2,mark phase=2]
			\addplot table {/data/Documents/tex/svn/crystal-gel/sample0.phd};
			\addplot table {/data/Documents/tex/svn/crystal-gel/sample1.phd};
			\addplot table {/data/Documents/tex/svn/crystal-gel/sample2.phd}[->] -- (rel axis cs:0.95,0.2);
			\addplot table {/data/Documents/tex/svn/crystal-gel/sample3.phd};
			\addplot table {/data/Documents/tex/svn/crystal-gel/sample4.phd};
			\addplot table {/data/Documents/tex/svn/crystal-gel/sample5.phd}[->] -- (rel axis cs:0.95,0.7);
			\end{scope}
			\addplot[black, dashed,no marks] file {/data/Documents/tex/svn/crystal-gel/gasliquid_sg.phd};% node[diamond, fill, inner sep=2pt] at (current plot begin){};
			\addplot[black, dashed,no marks] file {/data/Documents/tex/svn/crystal-gel/gasliquid_sl.phd};
			\addplot[black, no marks] file {/data/Documents/tex/svn/crystal-gel/gasliquid_bl.phd};
			\addplot[black, no marks] file {/data/Documents/tex/svn/crystal-gel/gasliquid_bg.phd};
			\addplot[fill=lightgray!50, no marks, draw=none] file {/data/Documents/tex/svn/crystal-gel/fluidcrystal_f.phd} node[above right] at (rel axis cs:0,0) {Fluid} -- (rel axis cs:0,0) \closedcycle;
			\addplot[fill=lightgray!50, no marks, draw=none] file {/data/Documents/tex/svn/crystal-gel/fluidcrystal_x.phd} %node[above left] (x) at (rel axis cs:1,0.5) {Crystal}  
			-| (rel axis cs:1,0) \closedcycle;
			%\draw[->] (x.base) --(rel axis cs:0.98,0.01);
			\addplot[only marks, mark=triangle] file{/data/Documents/tex/svn/crystal-gel/fluid_samples.phd};
	\end{axis}
	\end{tikzpicture}
	\includegraphics[height=11\baselineskip,clip=true,trim=0.5cm 0 0 0]{/data/Documents/tex/svn/crystal-gel/nature/fig2.pdf}

@@

\begin{frame}{Crystals outgrow liquid}
\vspace{\baselineskip}
\tikzsetnextfilename{crystal_fates}%
\begin{tikzpicture}
\begin{groupplot}[%
			group style={
				group name=g, group size=2 by 1,
				horizontal sep=4em,
				},
		width=0.5\linewidth,
		%height=0.5\linewidth,
	]
	\nextgroupplot[
		title={nuclei},
		xlabel={$t/10^3\tau_B$}, ylabel=\#,
		xmin=0, xmax=13.0, ymin=0,
		no marks,
		legend style={cells={anchor=base west}},
		]
	\addplot table[x expr={\thisrowno{0}/2.3e3}]{/data/Documents/tex/svn/crystal-gel/data/fig3a_1.dat} node[left] at (rel axis cs:1,0.2) {avg size};
	\addplot table[x expr={\thisrowno{0}/2.3e3}]{/data/Documents/tex/svn/crystal-gel/data/fig3a_2.dat} node[left] at (rel axis cs:1,0.6) {number};
	%\legend{average size, average number};

	\nextgroupplot[
		title={cluster size distribution},
		xlabel={$s$}, ylabel=$R_g/\sigma$,
		xmode=log, ymode=log,
		ytick={0.5, 1, 2, 4}, yticklabels={$\frac{1}{2}$, 1, 2, 4},
		domain=1:5e2,
		]
	\addplot[only marks, red, thick, mark=*] file{/data/Documents/tex/svn/crystal-gel/data/fig3d_sqrt_1.dat};
	\addplot[black, ultra thick] {0.522*x^(1/3)} node[below left] at (axis cs:9e2,2.5) {$D=3$};
	\addplot[gray, ultra thick] {0.426*x^(1/2.53)} node[pos=0.08,below right] {$D=2.53$};
\end{groupplot}
\end{tikzpicture}
\begin{center}
\tikzsetnextfilename{pathsX}\vspace{-0.5em}\input{pathsX.pgf}
\end{center}
\end{frame}

\begin{frame}{Dynamics: Bergeron > Ostwald}
\vspace{\baselineskip}
\includegraphics[width=\textwidth]{/data/Documents/tex/svn/crystal-gel/nature/fig4.pdf}
\end{frame}

>>>>

\institute[iLM]{iLM, Univ. Claude Bernard Lyon 1 and CNRS, France}
\title[crystal gel]{A novel route to the spontaneous formation of porous crystals via viscoelastic phase separation}
\author[M. Leocmach]{Mathieu Leocmach}
\date{30 June 2016}
\titlegraphic{
	\begin{tabu}{X[c]X[c]X[c]}
		\includegraphics[height=3\baselineskip]{presentation/Tsurusawa}&
		\includegraphics[height=3\baselineskip]{presentation/John}&
		\includegraphics[height=3\baselineskip]{presentation/Tanaka}\\
		Hideyo Tsurusawa & John Russo & Hajime Tanaka\\
		U. Tokyo & U. Bristol & U. Tokyo\\
	\end{tabu}

@@

\begin{frame}{Crystallisation}
	\tikzsetnextfilename{whyx}%
	\input{presentation/whyx.pgf}

@@

\begin{frame}{Let it snow!}
	\hfill Wegener-\alert{Bergeron}-Findeisen \alert{process}
	\begin{columns}[b]
	\column{0.4\textwidth}
	\includegraphics[width=\textwidth,clip=true,trim=0 0 0 1cm]{presentation/Pitter1.jpg}

	\vspace{1em}\includegraphics[width=\textwidth]{presentation/bergeron.jpg}
	\column{0.40\textwidth}
	\includegraphics[width=\textwidth,clip=true,trim=0 0 0.8mm 0]{presentation/queries-figure-1.jpg}

	\vspace{1em}\includegraphics[width=\textwidth]{presentation/OKC-Fallstreak.jpg}
	\end{columns}
\end{frame}

@@

	\bigskip
	\includegraphics[width=\textwidth]{../CNRS-2015/Renth_sedim.jpg}\\
	\textit{\footnotesize Poon PRL 1999, Renth PRE 2001}
	\begin{itemize}
	\item triple coexistence
	\item various kinetic paths
	\end{itemize}

	\column{0.45\textwidth}
	\includegraphics[width=\textwidth,clip=true,trim=0 0 0 4.5cm]{presentation/Renth_diag.pdf}
	\end{columns}
\end{frame}

\begin{frame}{Another class of gel? Crystal-gel?}
	\begin{itemize}
	\item Phase separation arrested by crystallisation
	\begin{description}
		\item[polymer blend] Tanaka \& Nishi \textit{PRL} 1985
		\item[simulations] Soga \textit{J.Chem. Phys.} 1999; Fortini \textit{PRE} 2008 
	\end{description}
	\item Spinodal then crystallisation
	\begin{description}
		\item[simulations] Pérez \textit{Langmuir} 2011
		\item[microgravity] (triple coexistence) Sabin \textit{PRL} 2012
	\end{description}
	\end{itemize}
	\includegraphics[width=\textwidth]{presentation/micrograv_Sabin2012}
\end{frame}

\begin{frame}{Experimental}
How to do that in 3D at particle level \alert{without a space station}?
\begin{itemize}
\item index matched + \alert{\SI{2.3}{\micro\metre} colloids} + confocal
\item density match + $T$-control
\item preparation protocol without flow
\end{itemize}
\bigskip
\begin{columns}
	\column{0.265\textwidth}
		Colloids+polymers\\
		{\footnotesize no screening
		\begin{itemize}
			\item Dispersed
			\item Homogeneous
		\end{itemize}
		\bigskip
		\begin{beamercolorbox}[rounded=true]{block body}PMMA + PS\\
		in decalin + CHB $\epsilon_r\approx5$\\
		$\kappa^{-1}>\SI{10}{\micro\metre}$
		\end{beamercolorbox}}
	\column{0.4\textwidth}
		\tikzsetnextfilename{chemin_gelification}%
		\input{presentation/chemin_gelification.pgf}
	\column{0.335\textwidth}
		\tikzsetnextfilename{cell}%
		\input{presentation/cell.pgf}
\end{columns}
\end{frame}

\begin{frame}{Exploring phase diagram}
	\vspace{\baselineskip}
	\tikzsetnextfilename{phdiag_cluster}%
	\begin{tikzpicture}[
		every axis/.style={
		xlabel absolute, every axis x label/.append style={anchor=base, yshift=-1em},
		%ylabel absolute, every axis y label/.append style={anchor=base, yshift=-0.5em}
		}]
	\pgfplotscreateplotcyclelist{samples}{%
	blue,mark=square*,\\%
	cyan,mark=square\\%
	red, thick, mark=*\\%
	red!65!yellow, mark=otimes\\%
	red!30!yellow, mark=oplus\\%
	red!65!black, mark=o\\%
	}%
	\begin{groupplot}[
		group style={
				group name=g, group size=2 by 2,
				horizontal sep=4em,
				vertical sep=3em,
				%x descriptions at=edge bottom,
			},
		cycle list name=samples,
		width=0.51\textwidth,
		height=0.5\linewidth,
		axis on top,
	]
	\nextgroupplot[
		title={phase diagram},
		xlabel={$\phi$}, ylabel={$c_p$ (\si{\milli\gram/\gram})},
		xmin=0,xmax=0.74,
		ymin=0, ymax=1.9, ytick={0,0.5,...,2},
		mark options={solid}
		]
		\begin{scope}[dotted, mark repeat=2,mark phase=2,<->]
		\addplot file {sample0.phd};
		\addplot file {sample1.phd};
		\addplot file {sample2.phd};
		\addplot file {sample3.phd};
		\addplot file {sample4.phd};
		\addplot file {sample5.phd};
		\end{scope}
		\addplot[black, dashed,no marks] file {gasliquid_sg.phd};% node[diamond, fill, inner sep=2pt] at (current plot begin){};
		\addplot[black, dashed,no marks] file {gasliquid_sl.phd};
		\addplot[black, no marks] file {gasliquid_bl.phd};
		\addplot[black, no marks] file {gasliquid_bg.phd};
		\addplot[fill=lightgray!50, no marks, draw=none] file {fluidcrystal_f.phd} node[above right] at (rel axis cs:0,0) {Fluid} -- (rel axis cs:0,0) \closedcycle;
		\addplot[fill=lightgray!50, no marks, draw=none] file {fluidcrystal_x.phd} node[above left] (x) at (rel axis cs:1,0.5) {Crystal}  -| (rel axis cs:1,0) \closedcycle;
		%\draw[gray] (axis cs:0.371290311343, 0.12299370925) -- (axis cs:0.680497991395,0.0372636873433);
		%\draw[gray, dotted] (axis cs:3.40152108798e-05,0.624739653238) -- (axis cs:0.722831684246, 0.0726528862772);
		\draw[->] (x.base) --(rel axis cs:0.98,0.01);
		\addplot[only marks, mark=triangle] file{fluid_samples.phd};

	\nextgroupplot[
		title={cluster size distribution},
		xlabel={$s$}, ylabel={$R_g/\sigma$},
		xmin=1, xmax=4e3,
		ymin=0.5, ymax=30,
		xmode=log, ymode=log, 
		clip mode=individual,
		]
		\addplot file{data/fig1b_sqrt_1.dat};
		\addplot file{data/fig1b_sqrt_2.dat};
		\addplot file{data/fig1b_sqrt_3.dat};
		\addplot file{data/fig1b_sqrt_4.dat};
		\addplot file{data/fig1b_sqrt_5.dat};
		\addplot[gray, ultra thick, domain=1:4e3] {0.629*x^(1/2.53)} node [left] at (rel axis cs:1,0.9){$D=2.53$};

@@

\begin{frame}{Outlier at later times}
	\vspace{\baselineskip}
	\tikzsetnextfilename{Sq_localphi}%
	\begin{tikzpicture}[
		every axis/.style={
		xlabel absolute, every axis x label/.append style={anchor=base, yshift=-1em},
		%ylabel absolute, every axis y label/.append style={anchor=base, yshift=-0.5em}
		}]
	\pgfplotscreateplotcyclelist{samples}{%
	blue,mark=square*,\\%
	cyan,mark=square\\%
	red, thick, mark=*\\%
	red!65!yellow, mark=otimes\\%
	red!30!yellow, mark=oplus\\%
	red!65!black, mark=o\\%
	}%
	\begin{groupplot}[
		group style={
				group name=g, group size=2 by 2,
				horizontal sep=4em,
				vertical sep=3em,
				%x descriptions at=edge bottom,
			},
		cycle list name=samples,
		width=0.51\textwidth,
		height=0.5\linewidth,
		axis on top,
	]
	\nextgroupplot[
		title={structure factor},
		xlabel={$q\sigma$}, ylabel={$S(q)$},
		xmode=log, ymode=log, xmin=0.2, xmax=20, ymin=0.1,
		restrict x to domain=-1.8:3, unbounded coords=discard, 
		%clip mode=individual
		]
		\addplot+[clip mode=individual] file{data/fig3c_1.dat};
		\addplot+[clip mode=individual] file{data/fig3c_2.dat};
		\addplot file{data/fig3c_3.dat};
		\addplot+[clip mode=individual] file{data/fig3c_4.dat};
		\addplot+[clip mode=individual] file{data/fig3c_5.dat};
		\addplot[black, ultra thick, domain=0.1:3] {2.14605*x^(-3)} node[pos=0.92,left=0.5em] {$D=3$};
		\addplot[gray, ultra thick, domain=0.1:3] {3.98797*x^(-2.53)} node [pos=0.65, above right] {$D=2.53$};

	\nextgroupplot[
		title={local volume fraction},
		xlabel={\# neighbours}, ylabel={$\phi$ [\%]},
		xmin=0, ymin=0, ytick={0,10,30,50},
		extra y ticks={64, 72}, extra y tick style={grid=major}, extra y tick label={},
		legend pos=north west, legend style={font=\footnotesize},
		no markers,
		/pgfplots/error bars/y dir=both, /pgfplots/error bars/y explicit,
		]
		\addplot table[y error=err]{data/vol_err_phi_0.10_cp_0.82.scaled};
		\addplot table[y error=err]{data/vol_err_phi_0.10_cp_1.36.scaled};
		\addplot table[y error=err]{data/vol_err_phi_0.25_cp_0.38.scaled};
		\addplot table[y error=err]{data/vol_err_phi_0.25_cp_0.48.scaled};
		\addplot table[y error=err]{data/vol_err_phi_0.25_cp_0.57.scaled};

@@

\begin{frame}{Real space: crystal gel!}
	\tikzsetnextfilename{phdiag_arrows}%
	\begin{tikzpicture}[
			every axis/.style={
			xlabel absolute, every axis x label/.append style={anchor=base, yshift=-1em},
			%ylabel absolute, every axis y label/.append style={anchor=base, yshift=-0.5em}
			}]
		\pgfplotscreateplotcyclelist{samples}{%
		blue,mark=square*,\\%
		cyan,mark=square\\%
		red, thick, mark=*\\%
		red!65!yellow, mark=otimes\\%
		red!30!yellow, mark=oplus\\%
		red!65!black, mark=o\\%
		}%
		\begin{axis}[
			cycle list name=samples,
			width=0.51\textwidth,
			height=0.5\linewidth,
			axis on top,
			xlabel={$\phi$}, ylabel={$c_p$ (\si{\milli\gram/\gram})},
			xmin=0,xmax=0.74,
			ymin=0, ymax=1.9, ytick={0,0.5,...,2},
			mark options={solid}
			]
			\begin{scope}[/pgfplots/skip coords between index={0}{1}, /pgfplots/skip coords between index={2}{3}]%[draw=none,mark repeat=2,mark phase=2]
			\addplot table {sample0.phd};
			\addplot table {sample1.phd};
			\addplot table {sample2.phd}[->] -- (rel axis cs:0.95,0.2);
			\addplot table {sample3.phd};
			\addplot table {sample4.phd};
			\addplot table {sample5.phd}[->] -- (rel axis cs:0.95,0.7);
			\end{scope}
			\addplot[black, dashed,no marks] file {gasliquid_sg.phd};% node[diamond, fill, inner sep=2pt] at (current plot begin){};
			\addplot[black, dashed,no marks] file {gasliquid_sl.phd};
			\addplot[black, no marks] file {gasliquid_bl.phd};
			\addplot[black, no marks] file {gasliquid_bg.phd};
			\addplot[fill=lightgray!50, no marks, draw=none] file {fluidcrystal_f.phd} node[above right] at (rel axis cs:0,0) {Fluid} -- (rel axis cs:0,0) \closedcycle;
			\addplot[fill=lightgray!50, no marks, draw=none] file {fluidcrystal_x.phd} %node[above left] (x) at (rel axis cs:1,0.5) {Crystal}  
			-| (rel axis cs:1,0) \closedcycle;
			%\draw[->] (x.base) --(rel axis cs:0.98,0.01);
			\addplot[only marks, mark=triangle] file{fluid_samples.phd};
	\end{axis}
	\end{tikzpicture}
	\includegraphics[height=11\baselineskip,clip=true,trim=0.5cm 0 0 0]{nature/fig2.pdf}

@@

\begin{frame}{Crystals outgrow liquid}
\vspace{\baselineskip}
\tikzsetnextfilename{crystal_fates}%
\begin{tikzpicture}
\begin{groupplot}[%
			group style={
				group name=g, group size=2 by 1,
				horizontal sep=4em,
				},
		width=0.5\linewidth,
		%height=0.5\linewidth,
	]
	\nextgroupplot[
		title={nuclei},
		xlabel={$t/10^3\tau_B$}, ylabel=\#,
		xmin=0, xmax=13.0, ymin=0,
		no marks,
		legend style={cells={anchor=base west}},
		]
	\addplot table[x expr={\thisrowno{0}/2.3e3}]{data/fig3a_1.dat} node[left] at (rel axis cs:1,0.2) {avg size};
	\addplot table[x expr={\thisrowno{0}/2.3e3}]{data/fig3a_2.dat} node[left] at (rel axis cs:1,0.6) {number};
	%\legend{average size, average number};

	\nextgroupplot[
		title={cluster size distribution},
		xlabel={$s$}, ylabel=$R_g/\sigma$,
		xmode=log, ymode=log,
		ytick={0.5, 1, 2, 4}, yticklabels={$\frac{1}{2}$, 1, 2, 4},
		domain=1:5e2,
		]
	\addplot[only marks, red, thick, mark=*] file{data/fig3d_sqrt_1.dat};
	\addplot[black, ultra thick] {0.522*x^(1/3)} node[below left] at (axis cs:9e2,2.5) {$D=3$};
	\addplot[gray, ultra thick] {0.426*x^(1/2.53)} node[pos=0.08,below right] {$D=2.53$};
\end{groupplot}
\end{tikzpicture}
\begin{center}
\tikzsetnextfilename{pathsX}\vspace{-0.5em}\input{presentation/pathsX.pgf}
\end{center}
\end{frame}

\begin{frame}{Dynamics: Bergeron > Ostwald}
\vspace{\baselineskip}
\includegraphics[width=\textwidth]{nature/fig4.pdf}
\end{frame}
